% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

\documentclass[11pt,a4paper]{article}

% ── Core Packages ──────────────────────────────────────────
\usepackage[margin=2cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{tcolorbox}
\usepackage{fontawesome5}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{setspace}
\usepackage{caption}
\usepackage{microtype}

\pgfplotsset{compat=1.18}
\usetikzlibrary{positioning,shapes.geometric,arrows.meta,calc,fit,shadows}

% ── Typography ─────────────────────────────────────────────
\setmainfont{Inter} 
\setsansfont{Inter}
\setmonofont{DejaVu Sans Mono}

% ── Colors ─────────────────────────────────────────────────
\definecolor{praxisBlue}{HTML}{007AFF}
\definecolor{praxisPurple}{HTML}{5856D6}
\definecolor{praxisGold}{HTML}{FFD60A}
\definecolor{praxisDark}{HTML}{050505}
\definecolor{praxisGray}{HTML}{1C1C1E}
\definecolor{praxisText}{HTML}{F2F2F7}

% ── Custom Boxes ───────────────────────────────────────────
\tcbuselibrary{skins,breakable}
\newtcolorbox{pitchbox}[1][]{
    enhanced, breakable, colback=praxisGray, colframe=praxisBlue,
    fonttitle=\bfseries\color{white}, title={#1},
    left=8pt, right=8pt, top=6pt, bottom=6pt
}

% ───────────────────────────────────────────────────────────
\begin{document}

\pagecolor{praxisDark}
\color{praxisText}

\begin{center}
\vspace*{1cm}
{\fontsize{60}{70}\selectfont\textbf{\textcolor{praxisBlue}{P}RAXIS}}\\[0.5cm]
{\LARGE\textbf{THE \$100B NETWORK STATE INFRASTRUCTURE}}\\[1.5cm]
\end{center}

\begin{pitchbox}[The Problem: The Coordination Crisis (2026)]
Legacy social graphs are dead. Nation-states are insolvent. Institutional trust has collapsed. We are facing a \textbf{Coordination Crisis} that existing networks cannot solve. We have traded intentionality for consumption, and the result is a global loneliness epidemic and a catastrophic failure of individual and collective Will.
\end{pitchbox}

\begin{pitchbox}[The Solution: Verified Intentionality]
Praxis is the first Social Operating System built for the \textbf{Architecture of Intent}. We transform the most valuable human data — **Intent** — into a verifiable asset. We synthesize the longevity of the \textbf{Church}, the exit-energy of the \textbf{Wandervogel}, and the resource pooling of the \textbf{Kibbutz} into a scalable digital market for human ambition.
\end{pitchbox}

\begin{center}
\begin{tikzpicture}[node distance=3.5cm]
    \node[draw=praxisBlue, circle, inner sep=10pt, fill=praxisGray] (A) {\small Market};
    \node[draw=praxisPurple, circle, inner sep=10pt, fill=praxisGray, right of=A] (B) {\small Monastery};
    \node[draw=praxisGold, circle, inner sep=10pt, fill=praxisGray, right of=B] (C) {\small Commune};
    \draw[thick, praxisPurple] (A) -- (B);
    \draw[thick, praxisPurple] (B) -- (C);
    \node[below=1.5cm of B, font=\Large\bfseries\color{praxisBlue}] {PRAXIS};
\end{tikzpicture}
\end{center}

\section*{The Competitive Moat: The Intention Graph}
Unlike the "Social Graph" (who you know) or the "Professional Graph" (what you've done), Praxis builds the \textbf{Intention Graph} (what you are going to do). By encoding ambition into semantic vectors and peer-verified trajectories, we are creating the most valuable data asset of the next 50 years. This is the infrastructure layer for the next era of human coordination.

\section*{Key Metrics \& The Network State Opportunity}
\begin{itemize}
    \item \textbf{Verified Reliability:} The $R$-score is the first non-gameable social credit system for decentralized trust.
    \item \textbf{High-Signal Alignment:} $S_{AB}$ semantic matching yields 10x higher engagement than interest-based tags.
    \item \textbf{Economic Engine:} 5\% fee on Accountability Escrow + SaaS subscriptions = FinTech-grade margins.
\end{itemize}

\begin{center}
\begin{tabularx}{\linewidth}{l X X X}
\toprule
\textbf{Metric} & \textbf{2026} & \textbf{2036} & \textbf{2076} \\
\midrule
Active Nodes & 50K & 10M & 500M+ \\
Verified Intent (Staked) & \$1M & \$1B & \$50B+ \\
Revenue (ARR + Fees) & \$4.8M & \$800M & \$40B+ \\
\bottomrule
\end{tabularx}
\end{center}

\vfill
\begin{center}
\textcolor{praxisBlue}{\rule{8cm}{1.5pt}} \\
\small\textcolor{praxisPurple}{Praxis Technologies · The Intentional Revolution · 2026}
\end{center}

\end{document}
